A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}). History matching is the process of building or adjusting one or more sets of models for a reservoir, such that the model(s) closely reproduces the past behaviour (flow rate, production volume or pressures) of a reservoir, and hopefully predict its future behaviour as well \cite{Rwechungura_2011}. It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.

>>>>

A number of recent research in reservoir engineering focus on  history matching problems (see \cite{Afra_2013, Insuasty_2017, Jafarpour_2009, Tavakoli_2010, Xiao_2018}). History matching is the process of building or adjusting one or more sets of models for a reservoir, such that reservoir models are able to closely reproduces past flow behaviour (\eg flow rate, production volume, pressure etc) in a geological formation, aiming to predict future flow behaviour with good accuracy \cite{Rwechungura_2011}. It is important to note that the model(s) referred to here could be a numerical model representing the system of parameters (\ie{variables}) which characterise the reservoir, or simply a model for parameterizing one of more components (\ie{variables}) of the system.
